8 tips for doing data visualization right.

### 2021-10-02 text/Rmd/8-tips/index.Rmd
Cleaned up some Rmd files
Fixed 1999 dates, part 1

---
title: "Recommendation: 8 tips for doing data visualization right."
author: "Steve Simon"
source: "http://blog.pmean.com/8-tips/"
date: "2014-05-03"
category: Recommendation
tags: Graphical display
output: html_document
---

@@

```{r}
library(knitr)
include_graphics("../../web/images/8-tips01.png")
```

>>>>

---
title: "8 tips for doing data visualization right."
author: "Steve Simon"
source: "http://blog.pmean.com/8-tips/"
date: "2014-05-03"
category: Recommendation
tags: Graphical display
output: html_document
---

@@

```{r}
library(knitr)
# include_graphics("../../web/images/8-tips01.png")
```
